---
title: "Coursera DDP Project Final MPG Cars"
author: "Mukund"
date: "11 February 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Developing Data Products course, Analysis of Miles per Gallon for various cars
This project is part of  final exercise Developing Data products course.
This course if 9th course of Data science specialization.

- This project is reated Shiny R. There is UI and server part of Shiny included in this project
- Documentation is created using R io_slide presentations

We use mtcars data set for analysis



## mtcars dataset has information 


```{r mtcars, echo = TRUE}
summary(mtcars)
```



## Slide with Plot

```{r}

library(ggplot2)
data("mtcars")
qplot(mtcars$hp, mtcars$mpg, color = mtcars$cyl,geom =c("point","smooth"),method = "lm", data = mtcars)

```

## Intreactive analytics for mtcars data

### We plot intereactive graphics and predict Horse power vs Miles per Gallon

- Instructions to user.
+ Use the check box to select model type 1 or 1 or both
+ Use the slider to select mpg of car
+ Press Submit button to see predicted Horsepower from either or both Models.
